Parameteric controls on responses to biogeochemical forcing in the CLM5

### 2018-11-19 SIfigs.tex

\end{document}

>>>>

    \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_TOTVEGC1__p2012.png}
     \caption{Influence of parametric variation on the impact of 15 years of CO$_{2}$ and N fertilization on vegetation carbon, across the Caxiuan\~a (CAX), Niwot Ridge (NWR), Harvard Forest (HVF) and Metolious MET) sites.}
     \label{VEGC CO2 and N respones 2001}
  \end{figure}

  \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_LEAFN1__p2012.png}
     \caption{Influence of parametric variation on the impact of 15 years of CO$_{2}$ and N fertilization on leaf nitrogen content ($N_{area}$), across the Caxiuan\~a (CAX), Niwot Ridge (NWR), Harvard Forest (HVF) and Metolious MET) sites.}
     \label{Leaf N CO2 and N respones 2001}
  \end{figure}
\end{document}
